### 2018-03-26 README.Rmd
Show time of most recent push to develop/docs
Update pkgdown

To install the developmental version of `infer`, make sure to install `remotes` first:

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.Date()`.

>>>>

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at https://infer.netlify.com.

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.
